%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Medad Rufus Newman (call me Rufus)} \\ \vspace{1pt}
    Chippenham, UK \\ \vspace{1pt}
    \small \href{tel:+447435651280}{ \raisebox{-0.1\height}\faPhone\ \underline{+44-7435651280} ~}
    \href{mailto:medad@medadnewman.co.uk}{\raisebox{-0.2\height}\faEnvelope\  \underline{medad@medadnewman.co.uk}} ~ 
    \href{medadnewman.co.uk}{\raisebox{-0.2\height}\faEnvelope\  \underline{medadnewman.co.uk}} ~ 
    \href{https://github.com/MedadRufus}{\raisebox{-0.2\height}\faGithub\ \underline{MedadRufus}} ~
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Imperial College London}{Sep. 2017 -- July 2021}
      {Masters in Design Engineering, 2:1}{London, UK}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dyson}{Hullavington, UK}
      {Graduate Software Engineer}{Feb 2022 - Present}
      \resumeItemListStart
        \resumeItem{Developing Bluetooth Low Energy (BLE) software for connectivity in C and Python.}
        \resumeItem{Implement embedded firmware unit testing using the Ceedling framework (Unity \& CMock).}
        \resumeItem{Documenting system architecture and software use instructions.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Ashburton Finance}{London, UK}
      {Founder}{Sep 2021 - Nov 2021}
      \resumeItemListStart
        \resumeItem{Founded a venture for lending of cryptocurrencies. Concept was based around aggregating flash loans from different flash loan providers (\href{https://github.com/Ashburton-Finance/flash-aggregator}{\color{blue}{Github link}}).}
        \resumeItem{Developed product on the Solana blockchain, using Smart Contracts, Typescript, Rust and Anchor framework.}
        \resumeItem{Moved on as it did not make much business sense to pursue it further at that time.}

      \resumeItemListEnd
  
    \resumeSubheading
      {Ion-O Tech}{London, UK}
      {Embedded Hardware/Software Engineer Intern}{June 2021 - Sep 2021}
      \resumeItemListStart
        \resumeItem{Worked in a team to develop a high performance, innovative electric bicycle.}
        \resumeItem{Worked on wireless connectivity, datalogging with custom hardware/firmware (C++); Designed and built battery packs as well.}
        \resumeItem{Created visualisation of battery performance/power consumption with InfluxDB \& Grafana for performance characterisation.}
        \resumeItem{Developed algorithms for energy consumption prediction, using physics models and machine learning.}
      \resumeItemListEnd

    \resumeSubheading
      {Onsee (formerly Pelation)}{London, UK}
      {Design Engineer Intern}{May 2020 - Sep 2020}
      \resumeItemListStart
        \resumeItem{Worked in a team developing a camera meant for cyclists; Worked on hardware/firmware for device and web interface (Django \& Python).}
        \resumeItem{Worked in embedded software development (C \& Python), playing a part in software architecture, version control, release process management, issue tracking, software testing and collaboration with hardware engineering colleagues to solve hardware/software issues.}
        \resumeItem{Did data analysis with Plotly dashboards and wrote programs for automated video processing.}
        \resumeItem{Carried out product testing, user interviews to get user feedback for improvements.}
        \resumeItem{Did mechanical design work, hand assembled prototypes, printed circuit board assembly, inspection and testing.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {\href{https://www.union.ic.ac.uk/guilds/icseds/2020/12/icspace22/}{\textbf{\large{\underline{High Altitude Balloon flights}}} \href{https://www.union.ic.ac.uk/guilds/icseds/2020/12/icspace22/}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{C, LoRaWAN}}}{2018 - present}
          \resumeItemListStart
            \resumeItem{\normalsize{Led a team to fly a small hydrogen balloon around the world on the Jet stream. Longest flight was for 22 days, flying over Japan, Canada, America and Euro­pe. The tracker we designed was powered by solar, and transmited position fixes via radio (LoRaWAN) to gateways worldwide.}}
          \resumeItemListEnd
                    
    \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ \normalsize{Python, C, C++, Java, Rust, Javascript(React)}} \\
     \textbf{\normalsize{Databases:}}{\normalsize{ MongoDB, InfluxDB }} \\
     \textbf{\normalsize{Visualisation tools:}}{\normalsize{ Grafana, Seaborn, Plotly }} \\
     \textbf{\normalsize{Technologies/Frameworks:}}{\normalsize{ Docker, Git, Linux }} \\
    }}
 \end{itemize}
 \vspace{-15pt}


\end{document}
