%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Medad Rufus Newman} \\ \vspace{1pt}
    Bristol, UK \\ \vspace{1pt}
    \small \href{tel:+447435651280}{ \raisebox{-0.1\height}\faPhone\ \underline{+44 7435651280} ~}
    \href{mailto:medad@medadnewman.co.uk}{\raisebox{-0.2\height}\faEnvelope\  \underline{medad@medadnewman.co.uk}} ~ 
    \href{https://medadnewman.co.uk}{\raisebox{-0.2\height}\faLink\  \underline{medadnewman.co.uk}} ~ 
    \href{https://github.com/MedadRufus}{\raisebox{-0.2\height}\faGithub\ \underline{MedadRufus}} ~
    \vspace{-8pt}
\end{center}


%-----------EXPERIENCE-----------------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dyson}{Hullavington, UK}
      {Graduate Software Engineer}{Feb 2022 - Present}
      \resumeItemListStart
        \resumeItem{Worked in 2 areas, Cloud software and Embedded software. }
        \resumeItem{Developed back-end cloud software for the MyDyson\texttrademark{} mobile app. Worked on updating APIs, adding monitoring, creating unittests/end-to-end tests for microservices and investigating new architectures for future products. Tech stack: .NET/C\#, Node.js, React, Docker, Cloudformation(AWS IaC). Hosted on AWS. }

        \resumeItem{Embedded Software work was to develop shared libraries for cryptography and Bluetooth connectivity that can be used across multiple products. Tech stack: C, Python, Ceedling, Behave.}



        \resumeItem{Active in Communities of Practice(CoPs), researching new techniques for automation and beta testing new ways of working.}

      \resumeItemListEnd
  
    \resumeSubheading
      {Ashburton Finance}{London, UK}
      {Founder}{Sep 2021 - Nov 2021}
      \resumeItemListStart
        \resumeItem{Worked on a venture for lending of cryptocurrencies. Concept was based around aggregating flash loans from different flash loan providers. \href{https://github.com/Ashburton-Finance/flash-aggregator}{\raisebox{-0.1\height}\faExternalLink }}
        \resumeItem{Tech stack: Rust, Node.js, Solana blockchain.}
        \resumeItem{Moved on as it did not make much business sense to pursue it further at that time.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Ion-O Tech}{London, UK}
      {Embedded Hardware/Software Engineer Intern}{June 2021 - Sep 2021}
      \resumeItemListStart
        \resumeItem{Worked in a team to develop a high performance, innovative electric bicycle.}
        \resumeItem{Developed hardware and firmware(C++) for wireless connectivity, telemetry.}
        \resumeItem{Designed and built battery packs, along with software for energy consumption prediction.}
        \resumeItem{Data visualisation with Grafana \& InfluxDB.}
      \resumeItemListEnd

    \resumeSubheading
      {Onsee (formerly Pelation)}{London, UK}
      {Design Engineer Intern}{May 2020 - Sep 2020}
      \resumeItemListStart
        \resumeItem{Worked in a team developing a camera meant for cyclists; Worked on hardware/firmware(C/Python) for device and web interface (Django).}
        \resumeItem{Carried out product testing, user interviews to get user feedback for improvements.}
        \resumeItem{MVP product launched in 4 months, a very short time for a hardware product.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Imperial College London}{London, UK}
      {Masters in Design Engineering, 2:1}{Sep. 2017 -- June 2021}
      \resumeItemListStart
        \resumeItem{Thesis on predicting E-bike energy consumption with machine learning {\href{https://medadnewman.co.uk/2021/10/06/e-bike-energy-consumption-prediction-with-past-data/}{\raisebox{-0.1\height}\faExternalLink }}. Using: XGBoost, Pandas, NumPy, SciPy. }
        \resumeItem{Subjects: Mechanics, Electronics, Materials and Manufacturing, Algorithms, Optimisation, Robotics, Human-Centred Design, Industrial Design and Business Strategy.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {\href{https://www.union.ic.ac.uk/guilds/icseds/2020/12/icspace22/}{\textbf{High altitude balloon flights} \href{https://www.union.ic.ac.uk/guilds/icseds/2020/12/icspace22/}{\raisebox{-0.1\height}\faExternalLink }} \large{\underline{}}}{2018 - present}
          \resumeItemListStart
            \resumeItem{\normalsize{Led a team to fly a small hydrogen balloon around the world on the Jet stream. Longest flight was for 22 days, flying over Japan, Canada, America and Europe. The tracker we designed was powered by solar, and transmitted position fixes via radio (LoRaWAN) to gateways worldwide.}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
    \resumeSubHeadingListStart

          \resumeItemListStart

    \resumeItem{\textbf{Languages:}{ Python, C, C\#, Node.js}}
     \resumeItem{\textbf{Databases:}{ MongoDB, InfluxDB, DynamoDB}}
     \resumeItem{\textbf{Visualisation tools:}{ Grafana, Seaborn, Plotly}}
     \resumeItem{\textbf{Technologies/Frameworks:}{ Docker, Git, Linux, SciPy, NumPy, Pandas, JupyterLab }}
    \resumeItem{ \textbf{Tooling:}{ Atlassian toolset, Github, Agile working}}
    
      \resumeItemListEnd
          \resumeSubHeadingListEnd

 \vspace{-15pt}

 %-----------PROGRAMMING SKILLS-----------

\end{document}
Developed hardware and firmware(C++) for wireless connectivity, telemetry.