%-------------------------
% Resume in Latex
% Author : Medad Newman
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://medadnewman.co.uk/}{\Large Medad Newman}} & Email : \href{mailto:medad@medadnewman.co.uk}{medad@medadnewman.co.uk}\\
  \href{https://medadnewman.co.uk/}{https://medadnewman.co.uk} & Mobile : +44 7435651280 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Imperial College London}{London, UK}
      {Masters in Design Engineering;  2:1 grade}{Sep. 2017 -- June. 2021}
      \resumeItemListStart
        \resumeItem{Subjects}
          {Mechanics, Electronics, Algorithms \& Data Structures, Optimisation, Robotics, Human-Centred Design, Industrial Design and Business Strategy.}
        \resumeItem{Thesis}
          {Thesis on predicting E-bike energy consumption with machine learning.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dyson}{Hullavington, UK}
      {Graduate Software Engineer}{Feb 2022 - Present}
      \resumeItemListStart
        \resumeItem{Bluetooth Low Energy}
          {Bluetooth Low Energy(BLE) is a low power communication protocol for connected devices. I write software running on Dyson products that communicate over Bluetooth LE.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Ashburton Finance}{London, UK}
      {Founder}{Sep 2021 - Nov 2021}
      \resumeItemListStart
        \resumeItem{Crypto Lending}
          {Founded a venture for lending of cryptocurrencies. Concept was based around aggregating flash loans from different flash loan providers(\href{https://github.com/Ashburton-Finance/flash-aggregator}{Github link})}
        \resumeItem{Smart Contracts/Blockchain}
          {Developed product on the Solana blockchain, using the latest tooling(Smart Contracts, Typescript/Rust programming, Anchor framework).}
      \resumeItemListEnd
  
    \resumeSubheading
      {Ion-O Tech}{London, UK}
      {Embedded Hardware/Software Engineer Intern}{June 2021 - Sep 2021}
      \resumeItemListStart
        \resumeItem{Electric Bike Development}
          {I worked in a team to develop a high performance, innovative electric bicycle.}
        \resumeItem{PCB Design}
          {Created an ESP32 based datalogger logging all relevant parameters from a moving E-bike.}
        \resumeItem{Data Visualisation}
          {Created visualisation dashboards of performance data from the product using Influxdb/Grafana.}
        \resumeItem{Embedded Software}
          {Wrote the software for datalogger, running FreeRTOS for scheduling and interfacing with several sensors.}
        \resumeItem{Battery Pack Design}
          {Designed custom battery packs and tested their performance, especially thermal characteristics.}
        \resumeItem{Energy Consumption Algorithms}
          {Developed algorithms for precisely predicting how much energy an electric bike will consume.}
      \resumeItemListEnd

    \resumeSubheading
      {Onsee (formerly Pelation)}{London, UK}
      {Design Engineer Intern}{May 2020 - Sep 2020}
      \resumeItemListStart
        \resumeItem{Rebo: Bike Camera}
          {Worked in a team developing a camera meant for cyclists; Worked on hardware/firmware for device and web interface(Django/Python).}
        \resumeItem{Embedded Software}
          {Wrote the software for the camera product, on 2 processors(Vision and Battery management). Code was written in C and in Python. Processors: Broadcom SoC and Attiny MCU.}
        \resumeItem{Battery Management Algorithms}
          {Wrote the algorithms for battery management, including State-of-Charge estimation, overvoltage/undervoltage protection, overcharge protection.}
        \resumeItem{Data Visualisation}
          {Created visualisation dashboards of data from the camera product, for performance analysis and fault detection.}
        \resumeItem{Video Processing}
          {Created scripts to cut, splice and watermark videos captured on the product.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Round-the-world Balloon project}
      {Led a team to fly a small hydrogen balloon around the world on the Jet stream. Longest flight was for 22 days, flying over Japan, Canada, America and Euro­pe. The tracker we designed was powered by solar, and transmited position fixes via radio(LoRaWAN) to gateways worldwide(\href{https://www.union.ic.ac.uk/guilds/icseds/2020/12/icspace22/}{launch report}).}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
    {Python, C, C++, Java, Rust, Typescript}
    \resumeSubItem{Technologies}
      {Docker, Git, Linux}
    \resumeSubItem{Visualisation tools}
      {Grafana, Seaborn, Plotly}
    \resumeSubItem{Databases}
      {MongoDB, InfluxDB}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
